Supplement to Manuscript for MADA Project

### 2023-03-20 code/analysis_code/statistical_analysis/Codes_for_statistical_analysis.Rmd
Updates addition

```{r}
# Using `mammogram_status` as the outcome and the remaining variables as the predictors
log_fit_fullmodel <- log_mod %>% fit(as.factor(mammogram_status) ~ as.factor(age) + as.factor(hispanic_status) + as.factor(income) + as.factor(education) + as.factor(marital_status) + as.factor(region_residence) + as.factor(insurance_status) + as.factor(health_status) + as.factor(usual_medicalcare_status) + as.factor(smoking_status) + as.factor(alcohol_status) + as.factor(diabetes_status), data = data_clean_main)
table2 <- tidy(log_fit_fullmodel)
table2
saveRDS(table2, file = (here("results", "final_analysis_result", "full_model.rds")))
```

@@

```{r}
# Using `mammogram_status` as the outcome and age & hispanic_status as predictors
log_fit_age_hispanic <- log_mod %>% fit(as.factor(mammogram_status) ~ as.factor(age) + as.factor(hispanic_status), data = data_clean_main)
tidy(log_fit_age_hispanic)
```

```{r}
# Using `mammogram_status` as the outcome and demographic characteristics variables as predictors
log_fit_demographic <- log_mod %>% fit(as.factor(mammogram_status) ~ as.factor(age) + as.factor(hispanic_status) + as.factor(income) + as.factor(education) + as.factor(marital_status) + as.factor(region_residence), data = data_clean_main)
tidy(log_fit_demographic)
```

```{r}
# Using `mammogram_status` as the outcome and the medical characteristics as the predictors
log_fit_medical <- log_mod %>% fit(as.factor(mammogram_status) ~ as.factor(insurance_status) + as.factor(health_status) + as.factor(usual_medicalcare_status) + as.factor(diabetes_status), data = data_clean_main)
tidy(log_fit_fullmodel)
```

```{r}
# Using `mammogram_status` as the outcome, and smoking & alcohol characteristics as the predictors
log_fit_smoking_alcohol <- log_mod %>% fit(as.factor(mammogram_status) ~ as.factor(smoking_status) + as.factor(alcohol_status), data = data_clean_main)
tidy(log_fit_smoking_alcohol)
```

>>>>

```{r}
# Using `mammogram_status` as the outcome and the remaining variables as the predictors
log_fit_fullmodel <- log_mod %>% fit(as.factor(mammogram_status) ~ as.factor(age) + as.factor(hispanic_status) + as.factor(income) + as.factor(education) + as.factor(marital_status) + as.factor(region_residence) + as.factor(insurance_status) + as.factor(health_status) + as.factor(usual_medicalcare_status) + as.factor(smoking_status) + as.factor(alcohol_status) + as.factor(diabetes_status), data = data_clean_main)
table2 <- tidy(log_fit_fullmodel)
table2
saveRDS(table2, file = (here("results", "statistical_analysis_result", "full_model.rds")))
```

@@

```{r}
# Using `mammogram_status` as the outcome and age & hispanic_status as predictors
log_fit_age_hispanic <- log_mod %>% fit(as.factor(mammogram_status) ~ as.factor(age) + as.factor(hispanic_status), data = data_clean_main)
table3 <- tidy(log_fit_age_hispanic)
saveRDS(table3, file = (here("results", "statistical_analysis_result", "age_hispanic_model.rds")))
```

```{r}
# Using `mammogram_status` as the outcome and demographic characteristics variables as predictors
log_fit_demographic <- log_mod %>% fit(as.factor(mammogram_status) ~ as.factor(age) + as.factor(hispanic_status) + as.factor(income) + as.factor(education) + as.factor(marital_status) + as.factor(region_residence), data = data_clean_main)
table4 <- tidy(log_fit_demographic)
saveRDS(table4, file = (here("results", "statistical_analysis_result", "demographic_model.rds")))
```

```{r}
# Using `mammogram_status` as the outcome and the medical characteristics as the predictors
log_fit_medical <- log_mod %>% fit(as.factor(mammogram_status) ~ as.factor(insurance_status) + as.factor(health_status) + as.factor(usual_medicalcare_status) + as.factor(diabetes_status), data = data_clean_main)
table5 <- tidy(log_fit_medical)
saveRDS(table5, file = (here("results", "statistical_analysis_result", "medical_model.rds")))
```

```{r}
# Using `mammogram_status` as the outcome, and smoking & alcohol characteristics as the predictors
log_fit_smoking_alcohol <- log_mod %>% fit(as.factor(mammogram_status) ~ as.factor(smoking_status) + as.factor(alcohol_status), data = data_clean_main)
table6 <- tidy(log_fit_smoking_alcohol)
saveRDS(table6, file = (here("results", "statistical_analysis_result", "smoking_alcohol_model.rds")))
```

### 2023-03-20 products/manuscript/Manuscript.qmd
Updates addition

```{r, warning = FALSE, message = FALSE}

library(here)
library(knitr)

@@

```{r, warning = FALSE, message = FALSE}
# Loading the `full_model.rds` table which was created during the statistical analysis process
result_table2 <- readRDS(here("results", "final_analysis_result", "full_model.rds"))
result_table2
```

>>>>

```{r, warning = FALSE, message = FALSE}
#| echo: FALSE
library(here)
library(knitr)

@@

```{r, warning = FALSE, message = FALSE}
#| echo: FALSE

# Loading the `full_model.rds` table which was created during the statistical analysis process
result_table2 <- readRDS(here("results", "statistical_analysis_result", "full_model.rds"))
print(result_table2, n = Inf, width = Inf)
```

### 2023-03-20 products/supplement/Supplementary_Material.qmd
Updates addition

---
title: "Supplement to Manuscript for MADA Project"
subtitle: ""
author: Shiwani Sapkota
date: "`r Sys.Date()`"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../dataanalysis_template_references.bib
csl: ../../vancouver.csl
---

@@

{{< pagebreak >}}

# Additional Method Details

Often, the main manuscript only allows for an overview description of the methods. Use the supplement to describe all your methods, models and approaches in a lot of detail. Reference specific parts of your code as needed.

{{< pagebreak >}}

# Additional results

Show additional results here. Those can be some useful exploratory/descriptive figures or tables, or results from additional analyses that didn't make it into the main text.

## Example additional result

@tbl-resulttable1 shows an additional table summarizing a model fit.

```{r}
#| label: tbl-resulttable1
#| tbl-cap: "Another fit table."
#| echo: FALSE
resulttable1 = readRDS(here("results","resulttable1.rds"))
knitr::kable(resulttable1)
```

@fig-result2 shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result2
#| fig-cap: "Height and weight."
#| echo: FALSE
knitr::include_graphics(here("results","height_weight.png"))
```

{{< pagebreak >}}

@@

Any additional discussion regarding the supplementary material/findings.

These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.

{{< pagebreak >}}

@@

>>>>

---
title: "Supplement to Manuscript for MADA Project"
subtitle: "Supplement Materials"
author: Shiwani Sapkota
date: "`r Sys.Date()`"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../dataanalysis_template_references.bib
csl: ../../vancouver.csl
---

@@

## Additional result

```{r}
#| label: Additional Table 1
#| tbl-cap: "Fit table using mammogram status as the outcome and age & hispanic_status as predictors."
#| echo: FALSE
additionaltable1 = readRDS(here("results", "statistical_analysis_result", "age_hispanic_model.rds"))
knitr::kable(additionaltable1)
```

```{r}
#| label: Additional Table 2
#| tbl-cap: "Fit table using mammogram status as the outcome and demographic characteristics variables as predictors."
#| echo: FALSE
additionaltable2 = readRDS(here("results", "statistical_analysis_result", "demographic_model.rds"))
knitr::kable(additionaltable2)
```

```{r}
#| label: Additional Table 3
#| tbl-cap: "Fit table using mammogram status as the outcome and the medical characteristics as the predictors."
#| echo: FALSE
additionaltable1 = readRDS(here("results", "statistical_analysis_result", "medical_model.rds"))
knitr::kable(additionaltable3)
```

```{r}
#| label: Additional Table 4
#| tbl-cap: "Fit table using mammogram status as the outcome and smoking & alcohol characteristics as the predictors."
#| echo: FALSE
additionaltable1 = readRDS(here("results", "statistical_analysis_result", "smoking_alcohol_model.rds"))
knitr::kable(additionaltable4)
```

@@

[**To be added]

@@

[**To be added]
